# Peer assignment 1

Luis Valdivieso

## Loading the data

```{r loading data}
activ = read.csv("/Users/lucho/Documents/ReproducibleResearch/Week1/RResearch1/activity.csv")
attach(activ)
head(activ)
```

## Analysis with missing data

```{r daily_statistics}
daysteps = by(activ[,1], date, sum)
daysteps= as.vector(daysteps)
hist(daysteps)
mean(daysteps,na.rm=TRUE)
median(daysteps,na.rm=TRUE)
```

Average daily activity pattern

```{r daily_activity_pattern}
mdaysteps = by(activ[,1], interval, mean,na.rm=TRUE)
plot(mdaysteps,type="l")
#Day interval with the maximum number of steps
mdaysteps[which.max(mdaysteps)]
```

## Analysis with imputed data

```{r}
# Number of missing values in the dataset
indexm = which(is.na(activ)==TRUE)
length(indexm)
daysm = unique(activ[indexm,2])
aux = na.omit(activ)
aux$date=factor(aux$date)
h = as.vector(by(aux[,1],aux$interval,mean))
afilled = activ
# Imputation
for (i in 1:length(daysm)){
  afilled[date==daysm[i],1] = h}
daystepsf = by(afilled[,1], date, sum)
daystepsf= as.vector(daystepsf)
hist(daystepsf)
mean(daystepsf)
median(daystepsf)
detach(activ)
```

The histogram now is more peaked, the mean does not change and the 
median equals the mean. This is expected, since we replaced the 
missing values by the mean number of steps in the intervals with information.

## Week and weekendays comparison

```{r}
library(timeDate)
WD = as.numeric(isWeekday(afilled$date, wday=1:5))
afilled = cbind(afilled,WD)
afilledw = afilled[WD==1,]
wmdaysteps = by(afilledw[,1], afilledw$interval, mean)
afilledwe = afilled[WD==0,]
wemdaysteps = by(afilledwe[,1], afilledwe$interval, mean)
par(mfrow = c(2,1))
plot(wmdaysteps,type="l")
title("Weekdays average number of steps per interval")
plot(wemdaysteps,type="l")
title("Weekendays average number of steps per interval")
```


